---
title: "DDS Case Study 2"
author: "Randy Kim"
date: "7/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyr)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(ggthemes)
library(skimr)
library(RColorBrewer)
library(readxl)
library(ggsci)
library(GGally)
library(e1071)
library(class)
library(caret)
library(corrplot)
```

```{r}
# had an issue with importing the excel file so had to save the salary as a csv.
data = read.csv("CaseStudy2-data.csv", header=TRUE)
salary = read.csv("CaseStudy2CompSet No Salary.csv", header=TRUE)
attrition = read.csv("CaseStudy2CompSet No Attrition.csv", header=TRUE)
```

```{r}
sapply(data,function(x) sum(is.na(x)))
str(data)
skim(data)
```

```{r}
data = subset(data, select = -c(EmployeeCount, EmployeeNumber, Over18, StandardHours))
data$Education = as.factor(data$Education)
data$EnvironmentSatisfaction = as.factor(data$EnvironmentSatisfaction)
data$JobInvolvement = as.factor(data$JobInvolvement)
data$JobLevel = as.factor(data$JobLevel)
data$JobSatisfaction = as.factor(data$JobSatisfaction)
data$PerformanceRating = as.factor(data$PerformanceRating)
data$RelationshipSatisfaction = as.factor(data$RelationshipSatisfaction)
data$StockOptionLevel = as.factor(data$StockOptionLevel)
data$WorkLifeBalance = as.factor(data$WorkLifeBalance)
```

# Attrition vs Education
```{r}
educ = data %>% count(Education,Attrition)
tapply(educ$n, educ$Education, FUN=sum)
educ %>% group_by(Education) %>% mutate(percent = n/sum(n) * 100) %>%
  ggplot(aes(x=Education,y=percent,fill=Attrition)) + geom_col(position="stack")
```

# Attrition vs Business Travel ** (22.14%)
```{r}
travel = data %>% count(BusinessTravel,Attrition)
tapply(travel$n, travel$BusinessTravel, FUN=sum)
travel %>% group_by(BusinessTravel) %>% mutate(percent = n/sum(n) * 100) %>%
  ggplot(aes(x=BusinessTravel,y=percent,fill=Attrition)) + geom_col(position="stack")
travel %>% spread(Attrition, n) %>% mutate(sum= Yes+No) %>% mutate(percent = Yes/sum * 100) %>%
  ggplot(aes(BusinessTravel,percent)) + geom_col() + coord_flip()
```

# Attrition vs Environment Satisfaction ** (24.42%)
```{r}
env = data %>% count(EnvironmentSatisfaction,Attrition)
tapply(env$n, env$EnvironmentSatisfaction, FUN=sum)
env %>% group_by(EnvironmentSatisfaction) %>% mutate(percent = n/sum(n) * 100) %>%
  ggplot(aes(x=EnvironmentSatisfaction,y=percent,fill=Attrition)) + geom_col(position="stack")
env %>% spread(Attrition, n) %>% mutate(sum = Yes+No) %>% mutate(percent = Yes/sum * 100) %>%
  ggplot(aes(EnvironmentSatisfaction,percent)) + geom_col() + coord_flip()
```

# Attrition vs Job Satisfcation ** (21.23%)
```{r}
sat = data %>% count(JobSatisfaction, Attrition)
sat %>% group_by(JobSatisfaction) %>% mutate(percent = n/sum(n) * 100) %>%
  ggplot(aes(x=JobSatisfaction,y=percent,fill=Attrition)) + geom_col(position="stack")
sat %>% spread(Attrition, n) %>% mutate(sum = Yes + No) %>% mutate(percent = Yes/sum * 100) %>%
  ggplot(aes(JobSatisfaction, percent)) + geom_col() + coord_flip()
```

# Attrition vs Relaionship Satisfcation (up) **
```{r}
relationship = data %>% count(RelationshipSatisfaction, Attrition)
relationship %>% group_by(RelationshipSatisfaction) %>% mutate(percent = n/sum(n) * 100) %>%
  ggplot(aes(x=RelationshipSatisfaction,y=percent,fill=Attrition)) + geom_col(position="stack")
```

# Attrition vs Department
```{r}
dep = data %>% count(Department, Attrition)
dep %>% group_by(Department) %>% mutate(percent = n/sum(n) * 100) %>%
  ggplot(aes(x=Department,y=percent,fill=Attrition)) + geom_col(position="stack")
dep %>% spread(Attrition, n) %>% mutate(sum = Yes + No) %>% mutate(percent = Yes/sum * 100) %>%
  ggplot(aes(Department, percent)) + geom_col() + coord_flip()
```

# Attrition vs Job Role (Sales Department has the highest attrition rate)***
```{r}
role = data %>% count(JobRole, Attrition)
role %>% group_by(JobRole) %>% mutate(percent = n/sum(n) * 100) %>%
  ggplot(aes(x=JobRole,y=percent,fill=Attrition)) + geom_col(position="stack") + coord_flip()
role %>% spread(Attrition, n) %>% mutate(sum = Yes + No) %>% mutate(percent = Yes/sum * 100) %>%
  ggplot(aes(JobRole, percent,fill=JobRole)) + geom_col() + coord_flip() + xlab("") + ylab("Percent (%)")

dep_role = data %>% count(JobRole, Department, Attrition)
dep_role %>% spread(Attrition, n) %>% mutate(sum = Yes + No) %>% mutate(percent = Yes/sum * 100) %>%
  ggplot(aes(JobRole, percent, fill = Department)) + geom_col() + coord_flip() + xlab("") + ylab("Rating (%)")

# Job involvement
role_inv = data %>% count(JobRole, JobInvolvement, Attrition)
role_inv %>% ggplot(aes(JobRole, n, fill = Attrition)) + geom_col() + coord_flip()

role_inv %>% spread(Attrition, n) %>% mutate(sum = Yes + No) %>% mutate(percent = Yes/sum * 100) %>%
  ggplot(aes(JobRole, percent, fill = JobInvolvement)) + geom_col() + coord_flip()

data %>% select(JobInvolvement, JobRole) %>% ggpairs()
```

# Attrition vs Distance from Home
```{r}
home = subset(data, select = c(DistanceFromHome, Attrition))
home = home %>% mutate(distance = cut(DistanceFromHome, breaks = c(0,7,14,29),
                       labels=c("Short", "Medium", "Long")))
homedistance = home %>% count(distance, Attrition)
homedistance %>% spread(Attrition, n) %>% mutate(sum = Yes + No) %>% mutate(percent = Yes/sum * 100) %>% 
  ggplot(aes(distance,percent,fill = "Yes")) + geom_col()
```

# Attrition vs Age
```{r}
age = data %>% count(Age, Attrition)
age %>% ggplot(aes(x=Age, y=Attrition, fill = Attrition)) + geom_point()

age %>% spread(Attrition, n) %>% mutate(sum = Yes+No) %>% mutate(percent = Yes/sum * 100) %>% ggplot(aes(Age,percent)) + geom_point() + geom_smooth()

age$logage = log(age$Age)
age %>% spread(Attrition, n) %>% mutate(sum = Yes+No) %>% mutate(percent = Yes/sum * 100) %>% ggplot(aes(logage,percent)) + geom_point() + geom_smooth()
```

# Monthly Income vs Age with Attrition == "Yes"
```{r}
data %>% select(Attrition, MonthlyIncome, Age, Department) %>% filter(Attrition == "Yes") %>% 
  ggplot(aes(x=Age, y=MonthlyIncome)) + 
  geom_rect(aes(xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = median(data$MonthlyIncome), fill = "Median Monthly Income")) +
  geom_rect(aes(xmin = -Inf, xmax = Inf, ymin = median(data$MonthlyIncome), ymax = mean(data$MonthlyIncome), fill = "Mean Monthly Income")) +
  geom_rect(aes(xmin = 18, xmax = 35, ymin = -Inf, ymax = median(data$MonthlyIncome), fill = "Age between 18 and 35")) +
  geom_rect(aes(xmin = -Inf, xmax = Inf, ymin = mean(data$MonthlyIncome), ymax = Inf, fill = "Above Mean Monthly Income")) +  scale_fill_brewer(palette = "Pastel1", name = "Scale") +
  geom_point(position="jitter",aes(color = Department)) +
  ggtitle("Monthly Income vs Age with Attrition = Yes") +
  xlab("Year") + ylab("Income ($)") + theme_bw() +
  geom_hline(aes(yintercept = mean(data$MonthlyIncome), linetype = "Mean Income ($6390,26)"),size = 0.75, colour = "red") +
  geom_hline(aes(yintercept = median(data$MonthlyIncome), linetype = "Median Income ($4945.5)"),size = 0.75, color = "blue") +
  scale_linetype_manual(name = "", values = c(2,2), guide = guide_legend(override.aes = list(color = c("red","blue"))))

data %>% select(Attrition, MonthlyIncome, Age) %>% 
  ggplot(aes(x=Age, y=MonthlyIncome)) + 
  geom_rect(aes(xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = median(data$MonthlyIncome), fill = "Median Monthly Income")) +
  geom_rect(aes(xmin = -Inf, xmax = Inf, ymin = median(data$MonthlyIncome), ymax = mean(data$MonthlyIncome), fill = "Mean Monthly Income")) +
  geom_rect(aes(xmin = -Inf, xmax = Inf, ymin = mean(data$MonthlyIncome), ymax = Inf, fill = "Above Mean Monthly Income")) +
  scale_fill_brewer(palette = "Pastel1", name = "Scale") +
  geom_point(position="jitter",aes(color = Attrition)) +
  ggtitle("Monthly Income vs Age with Attrition") +
  xlab("Year") + ylab("Income ($)") + theme_bw() +
  geom_hline(aes(yintercept = mean(data$MonthlyIncome), linetype = "Mean Income ($6390,26)"),size = 0.75, colour = "red") +
  geom_hline(aes(yintercept = median(data$MonthlyIncome), linetype = "Median Income ($4945.5)"),size = 0.75, color = "blue") +
  scale_linetype_manual(name = "", values = c(2,2), guide = guide_legend(override.aes = list(color = c("red","blue"))))

```


# Attrition vs Working Years
```{r}
years = data %>% count(TotalWorkingYears, Attrition)
years %>% spread(Attrition, n) %>% mutate(sum = Yes+No) %>% mutate(percent = Yes/sum * 100) %>%
  ggplot(aes(TotalWorkingYears,percent)) + geom_point() + geom_smooth()
```

# Attrition vs Job Involvement *** (46.81%)
```{r}
job_inv = data %>% count(JobInvolvement, Attrition)
job_inv %>% group_by(JobInvolvement) %>% mutate(percent = n/sum(n) * 100) %>%
  ggplot(aes(x=JobInvolvement,y=percent,fill=Attrition)) + geom_col(position = "stack")
job_inv %>% spread(Attrition, n) %>% mutate(sum = Yes+No) %>% mutate(percent = Yes/sum * 100) %>%
  ggplot(aes(JobInvolvement,percent)) + geom_col(fill="darkblue") + ggtitle("Attrition vs Job Involvement") +
  xlab("Job Involvement Rating") + ylab("Rating (%)")
```

# Attrition vs Job Level ** (26.14%)
```{r}
job_level = data %>% count(JobLevel, Attrition)
job_level%>% group_by(JobLevel) %>% mutate(percent = n/sum(n) * 100) %>%
  ggplot(aes(x=JobLevel,y=percent,fill=Attrition)) + geom_col(position = "stack")
job_level %>% spread(Attrition, n) %>% mutate(sum = Yes+No) %>% mutate(percent = Yes/sum * 100) %>%
  ggplot(aes(JobLevel,percent)) + geom_col()
```


# Attrition vs Monthly Income
```{r}
income = data %>% count(MonthlyIncome, Attrition)
income %>% group_by(MonthlyIncome) %>% mutate(percent = n/sum(n) * 100) %>%
  ggplot(aes(x=MonthlyIncome,y=percent)) + geom_point(position = "jitter",aes(colour = factor(Attrition)))
income %>% spread(Attrition, n) %>% mutate(sum = Yes+No) %>% mutate(percent = Yes/sum * 100) %>%
  ggplot(aes(MonthlyIncome,percent)) + geom_point()
```

# Attrition vs Over Time *** (31.74%)
```{r}
overtime = data %>% count(OverTime, Attrition)
overtime %>% group_by(OverTime) %>% mutate(percent = n/sum(n) * 100) %>%
  ggplot(aes(x=OverTime,y=percent,fill = Attrition)) + geom_col()
overtime %>% spread(Attrition, n) %>% mutate(sum = Yes+No) %>% mutate(percent = Yes/sum * 100) %>%
  ggplot(aes(OverTime,percent)) + geom_col(fill="darkblue") + ggtitle("Attrition vs Over Time") +
  xlab("") + ylab("")
```

# Attrition vs Performance Rating
```{r}
performance = data %>% count(PerformanceRating, Attrition)
performance %>% group_by(PerformanceRating) %>% mutate(percent = n/sum(n) * 100) %>%
  ggplot(aes(x=PerformanceRating,y=percent,fill = Attrition)) + geom_col()
```

# Attrition vs Work Life Balance *** (35.41%)
```{r}
life = data %>% count(WorkLifeBalance, Attrition)
life %>% group_by(WorkLifeBalance) %>% mutate(percent = n/sum(n) * 100) %>%
  ggplot(aes(x=WorkLifeBalance,y=percent,fill=Attrition)) + geom_col()
life %>% spread(Attrition, n) %>% mutate(sum = Yes+No) %>% mutate(percent = Yes/sum * 100) %>%
  ggplot(aes(WorkLifeBalance,percent)) + geom_col(fill="darkblue") + ggtitle("Attrition vs Work Life Balance") +
  xlab("Work Life Balance Rating") + ylab("Rating (%)")
```


# kNN model with Job Involvement, Work Life Balance, Environment Satisfaction, Job Level
## Accuracy : 83.8%
## Sensitivity : 84.04%
## Specificity : NA
```{r}
iterations = 100
splitPerc = 0.7
numks = 50
set.seed(7)

masterAcc = matrix(nrow = iterations, ncol = numks)
masterSens = matrix(nrow = iterations, ncol = numks)
masterSpec = matrix(nrow = iterations, ncol = numks)

for(i in 1:iterations){
  set.seed(i)
  trainIndices = sample(1:dim(data)[1],round(splitPerc * dim(data)[1]))
  train = data[trainIndices,]
  test = data[-trainIndices,]
  for(j in 1:numks)
  {
    classifications = knn(train[,c("JobInvolvement","WorkLifeBalance","EnvironmentSatisfaction","JobLevel")],
                        test[,c("JobInvolvement","WorkLifeBalance","EnvironmentSatisfaction","JobLevel")],
                        as.factor(train$Attrition), 
                        prob = TRUE, 
                        k = j)
    CM = confusionMatrix(table(as.factor(test$Attrition),classifications))
    masterAcc[i,j] = CM$overall[1]
    masterSens[i,j] = CM$byClass[1]
    masterSpec[i,j] = CM$byClass[2]
  }
}

CM
mean(masterAcc)
mean(masterSens)
mean(masterSpec)
```

# kNN model with Job Involvement, Work Life Balance, Environment Satisfaction
## Accuracy : 83.8%
## Sensitivity : 84.0%
## Specificity : NA
```{r}
iterations = 100
splitPerc = 0.7
numks = 50
set.seed(7)

masterAcc = matrix(nrow = iterations, ncol = numks)
masterSens = matrix(nrow = iterations, ncol = numks)
masterSpec = matrix(nrow = iterations, ncol = numks)

for(i in 1:iterations){
  set.seed(i)
  trainIndices = sample(1:dim(data)[1],round(splitPerc * dim(data)[1]))
  train = data[trainIndices,]
  test = data[-trainIndices,]
  for(j in 1:numks)
  {
    classifications = knn(train[,c("JobInvolvement","WorkLifeBalance","EnvironmentSatisfaction")],
                        test[,c("JobInvolvement","WorkLifeBalance","EnvironmentSatisfaction")],
                        as.factor(train$Attrition), 
                        prob = TRUE, 
                        k = j)
    CM = confusionMatrix(table(as.factor(test$Attrition),classifications))
    masterAcc[i,j] = CM$overall[1]
    masterSens[i,j] = CM$byClass[1]
    masterSpec[i,j] = CM$byClass[2]
  }
}

CM
mean(masterAcc)
mean(masterSens)
mean(masterSpec)
```

#Naive Bayes Test
```{r}
iteartions = 100
splitPerc = 0.7
numks = 50

trainIndices = sample(seq(1:length(data$ID)), round(.7 * length(data$ID)))
train = data[trainIndices,]
test = data[-trainIndices,]
model = naiveBayes(train[,c("JobInvolvement","WorkLifeBalance","OverTime","JobRole")],
                   train$Attrition)
CM = confusionMatrix(table(factor(test$Attrition,labels = c("No","Yes")),
                           predict(model,test[,c("JobInvolvement","WorkLifeBalance","OverTime","JobRole")])))
CM


trainIndices = sample(seq(1:length(data$ID)), round(.7 * length(data$ID)))
train = data[trainIndices,]
test = data[-trainIndices,]
model = naiveBayes(train[,c("JobInvolvement","WorkLifeBalance","OverTime")],
                   train$Attrition)
CM = confusionMatrix(table(factor(test$Attrition,labels = c("No","Yes")),
                           predict(model,test[,c("JobInvolvement","WorkLifeBalance","OverTime")])))
CM

trainIndices = sample(seq(1:length(data$ID)), round(.7 * length(data$ID)))
train = data[trainIndices,]
test = data[-trainIndices,]
model = naiveBayes(train[,c("JobInvolvement","WorkLifeBalance","OverTime","Age")],
                   train$Attrition)
CM = confusionMatrix(table(factor(test$Attrition,labels = c("No","Yes")),
                           predict(model,test[,c("JobInvolvement","WorkLifeBalance","OverTime","Age")])))
CM


```

# Bayes Model with Job Involvement, Work Life Balance, Over Time, Job Role
## Accuracy : 85.79%
## Sensitivity : 86.76%
## Specificity : 69.0%
```{r}
iteartions = 100
splitPerc = 0.7
numks = 50

masterAcc = matrix(nrow = iterations, ncol = numks)
masterSens = matrix(nrow = iterations, ncol = numks)
masterSpec = matrix(nrow = iterations, ncol = numks)

for(j in 1:iterations)
{
  set.seed(j)
  trainIndices = sample(seq(1:length(data$ID)), round(.7 * length(data$ID)))
  train = data[trainIndices,]
  test = data[-trainIndices,]
  
  for(i in 1:numks)
  {
    model = naiveBayes(train[,c("JobInvolvement","WorkLifeBalance","OverTime","JobRole")],
                   train$Attrition)
    CM = confusionMatrix(table(factor(test$Attrition,labels = c("No","Yes")),
                               predict(model,test[,c("JobInvolvement","WorkLifeBalance","OverTime","JobRole")])))
    masterAcc[j,i] = CM$overall[1]
    masterSens[j,i] = CM$byClass[1]
    masterSpec[j,i] = CM$byClass[2]
  }
}

CM
mean(masterAcc)
mean(masterSens)
mean(masterSpec)

```

# Bayes model with Job Involvement, Work Life Balance, Over Time
## Accuracy : 84.48%
## Sensitivity : 85.31%
## Specificity : 59.06%
```{r}
masterAcc = matrix(nrow = iterations, ncol = numks)
masterSens = matrix(nrow = iterations, ncol = numks)
masterSpec = matrix(nrow = iterations, ncol = numks)

iteartions = 100
splitPerc = 0.7
numks = 50

for(j in 1:iterations)
{
  set.seed(j)
  trainIndices = sample(seq(1:length(data$ID)), round(.7 * length(data$ID)))
  train = data[trainIndices,]
  test = data[-trainIndices,]
  
  for(i in 1:numks)
  {
    model = naiveBayes(train[,c("JobInvolvement","WorkLifeBalance","OverTime")],
                   train$Attrition)
    CM = confusionMatrix(table(factor(test$Attrition,labels = c("No","Yes")),
                               predict(model,test[,c("JobInvolvement","WorkLifeBalance","OverTime")])))
    masterAcc[j,i] = CM$overall[1]
    masterSens[j,i] = CM$byClass[1]
    masterSpec[j,i] = CM$byClass[2]
  }
}

CM
mean(masterAcc)
mean(masterSens)
mean(masterSpec)

```
```{r}
attrition = subset(attrition, select = -c(EmployeeCount, EmployeeNumber, Over18, StandardHours))
attrition$EnvironmentSatisfaction = as.factor(attrition$EnvironmentSatisfaction)
attrition$JobInvolvement = as.factor(attrition$JobInvolvement)
attrition$JobLevel = as.factor(attrition$JobLevel)
attrition$WorkLifeBalance = as.factor(attrition$WorkLifeBalance)
```

#Final
# Bayes Model with Job Involvement, Work Life Balance, Over Time, Job Role
## Accuracy : 85.79%
## Sensitivity : 86.76%
## Specificity : 69.0%
```{r}
model = naiveBayes(train[,c("JobInvolvement","WorkLifeBalance","OverTime","JobRole")],
                   train$Attrition,labels = c("No","Yes"))
attrition$Attrition = predict(model,attrition[,c("JobInvolvement","WorkLifeBalance","OverTime","JobRole")])
output = attrition %>% select(ID, Attrition)
write.csv(output, file="Case2PredictionsKim Attrition.csv",row.names = FALSE)
```

```{r}
col <- colorRampPalette(c("#BB4444", "#EE9988", "#FFFFFF", "#77AADD", "#4477AA"))
data %>% select_if(is.numeric) %>% cor() %>%
  corrplot(method="color", 
           col=col(200), 
           number.digits=2,
           number.cex=0.5, 
           type="upper", 
           order="hclust", 
           addCoef.col = "black",
           tl.col="black", 
           tl.srt=45,
           sig.level = 0.01, 
           insig = "blank", 
           diag=FALSE 
         )

data %>% select(Age, MonthlyIncome) %>% ggpairs() #.484
data %>% select(YearsInCurrentRole, MonthlyIncome) %>% ggpairs() #.362
data %>% select(YearsAtCompany, MonthlyIncome) %>% ggpairs() # .491
data %>% select(YearsWithCurrManager, MonthlyIncome) %>% ggpairs() # .328
data %>% select(YearsSinceLastPromotion, MonthlyIncome) %>% ggpairs() # .316
data %>% select(TotalWorkingYears, MonthlyIncome) %>% ggpairs() #.779

data %>% select(Department,Education,MonthlyIncome) %>% ggpairs()
data %>% select(JobInvolvement,JobLevel,MonthlyIncome) %>% ggpairs()
data %>% select(JobRole,PerformanceRating,MonthlyIncome) %>% ggpairs()
```
# Total Working Years, Years at Company, Age, Years in Current Role, Job Level, Education(?)
```{r}
data %>% ggplot(aes(TotalWorkingYears, MonthlyIncome)) + geom_point() + geom_smooth() +
  ggtitle("Total Working Years vs Monthly Income") + xlab("Years") + ylab("Income ($)")
data %>% ggplot(aes(YearsAtCompany,MonthlyIncome)) + geom_point() + geom_smooth() +
  ggtitle("Years At Compnay vs Monthly Income") + xlab("Years") + ylab("Income ($)")
data %>% ggplot(aes(Age, MonthlyIncome)) + geom_point() + geom_smooth() +
  ggtitle("Age vs Monthly Income") + xlab("Years") + ylab("Income ($)")
data %>% ggplot(aes(YearsInCurrentRole, MonthlyIncome)) + geom_point() + geom_smooth()
data %>% ggplot(aes(JobLevel, MonthlyIncome)) + geom_point() + geom_smooth() +
  ggtitle("Job Level vs Monthly Income") + xlab("Job Level") + ylab("Income ($)")
data %>% ggplot(aes(Education, MonthlyIncome)) + geom_point() + geom_smooth()

# totalworkingyears
# Years at company
# age
# JobLevel

```

```{r}
trainIndices = sample(seq(1,dim(data)[1]),round(.7*dim(data)[1]), replace=FALSE)
train = data[trainIndices,]
test = data[-trainIndices,]

# model 1
fit = lm(MonthlyIncome ~ TotalWorkingYears, data = train)
summary(fit)
confint(fit)

preds = predict(fit, newdata = test)
MSPE = mean((test$MonthlyIncome - preds)^2)
sqrt(MSPE)
# RMSE = 2807.818

# model 2
fit2 = lm(MonthlyIncome ~ TotalWorkingYears + YearsAtCompany, data = train)
summary(fit2)
confint(fit2)

preds = predict(fit2, newdata = test)
MSPE = mean((test$MonthlyIncome - preds)^2)
sqrt(MSPE)
# RMSE = 2807.682

# model 3
fit3 = lm(MonthlyIncome ~ TotalWorkingYears + YearsAtCompany + JobRole + JobLevel, data = train)
summary(fit3)
confint(fit3)

preds = predict(fit3, newdata = test)
MSPE = mean((test$MonthlyIncome - preds)^2)
sqrt(MSPE)
# RMSE = 978.4626

# model 4
fit4 = lm(MonthlyIncome ~ TotalWorkingYears + YearsAtCompany + JobRole + JobLevel + Age, data = train)
summary(fit4)
confint(fit4)

preds = predict(fit4, newdata = test)
MSPE = mean((test$MonthlyIncome - preds)^2)
sqrt(MSPE)


# testing models with different seeds
iteartions = 100
splitPerc = 0.7
numks = 50

masterRMSE = matrix(nrow = iterations, ncol = numks)
masterRMSE2 = matrix(nrow = iterations, ncol = numks)
masterRMSE3 = matrix(nrow = iterations, ncol = numks)
masterRMSE4 = matrix(nrow = iterations, ncol = numks)

for(j in 1:iterations)
{
  set.seed(j)
  trainIndices = sample(seq(1,dim(data)[1]),round(.7*dim(data)[1]), replace=FALSE)
  train = data[trainIndices,]
  test = data[-trainIndices,]
  
  for(i in 1:numks)
  {
    #model 1
    fit = lm(MonthlyIncome ~ TotalWorkingYears, data = train)
    preds = predict(fit, newdata = test)
    MSPE = mean((test$MonthlyIncome - preds)^2)
    masterRMSE[j,i] = sqrt(MSPE)
    
    #model 2
    fit2 = lm(MonthlyIncome ~ TotalWorkingYears + YearsAtCompany, data = train)
    preds2 = predict(fit2, newdata = test)
    MSPE2 = mean((test$MonthlyIncome - preds2)^2)
    masterRMSE2[j,i] = sqrt(MSPE2)
    
    #model 3
    fit3 = lm(MonthlyIncome ~ TotalWorkingYears + YearsAtCompany + JobRole + JobLevel, data = train)
    preds3 = predict(fit3, newdata = test)
    MSPE3 = mean((test$MonthlyIncome - preds3)^2)
    masterRMSE3[j,i] = sqrt(MSPE3)
    
    #model 4
    fit4 = lm(MonthlyIncome ~ TotalWorkingYears + YearsAtCompany + JobRole + JobLevel + Age, data = train)
    preds4 = predict(fit4, newdata = test)
    MSPE4 = mean((test$MonthlyIncome - preds4)^2)
    masterRMSE4[j,i] = sqrt(MSPE4)
  }
}

masterRMSE
mean(masterRMSE)
#2878.695

masterRMSE2
mean(masterRMSE2)
#2887.675

masterRMSE3
mean(masterRMSE3)
#1016.014
#p-value <2.2e-16
#adjusted R-square 0.9505

masterRMSE4
mean(masterRMSE4)
#1017.168
#p-value <2.2e-16
#adjusted R-square 0.9504


#AIC and BIC
fit5 = lm(MonthlyIncome ~. , data = train)
testing = step(fit5, direction = "both")
testing2 = step(fit5, k=2)
testing3 = step(fit5, k=nrow(log(train)))
```

```{r}
salary = subset(salary, select = -c(EmployeeCount, EmployeeNumber, Over18, StandardHours))
salary$JobLevel = as.factor(salary$JobLevel)
```

# Predicted Salaries
```{r}
model = lm(MonthlyIncome ~ TotalWorkingYears + YearsAtCompany + JobRole + JobLevel, data = train)
salary$MonthlyIncome = predict(model, newdata = salary)
output = salary %>% select(ID, MonthlyIncome)
write.csv(output, file = "Case2PredictionsKim Salary.csv", row.names = FALSE)
```



















